---
title: "DM3"
author: "Vibhav Mayekar,Pratik Sharma, Jitesh Patil"
date: "2/27/2022"
output: word_document
---


```{r}
#install.packages('readxl')
#install.packages('readxl')
#install.packages("randomForest")
#install.packages("caret")
#install.packages("ROCR")
#install.packages("corrplot")
library(readxl)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(dplyr)
library(corrplot)
library(apaTables)
library(rpart)
library(rpart.plot)
library(psych)
library(randomForest)
library(caret)
library(ROCR)
library(ISLR)
#install.packages('readxl')
#install.packages("randomForest")
#install.packages("caret")
#install.packages("ROCR")

f<-file.choose()
Retention_modeling <- read_excel(f)
#Retention_modeling <- read_excel("Retention modeling.xlsx",sheet = 2)
##View(Retention_modeling)
rm1 <- Retention_modeling
ogdata <- Retention_modeling
View(rm1)
```
```{r}
rm1 <- rm1[-(2390:2392),,drop=FALSE]
ogdata <- ogdata[-(2390:2392),,drop=FALSE]



rm1$Retained.in.2012. <- as.factor(ifelse(rm1$Retained.in.2012. == 1, "Retained" , "Not Retained"))

rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "Elementary->Elementary", "E->E")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "Middle->Middle", "M->M")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "High->High", "H->H")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "Undefined->Undefined", "U->U")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType,
          rm1$SchoolGradeType == "Middle->Undefined", "M->U")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType,
          rm1$SchoolGradeType == "Elementary->Middle", "E->M")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "Middle->High", "M->H")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType,
          rm1$SchoolGradeType == "Elementary->High", "E->H")
rm1$SchoolGradeType <- 
  replace(rm1$SchoolGradeType, 
          rm1$SchoolGradeType == "Elementary->Undefined", "E->U")

rm1$Is.Non.Annual. <- as.factor(ifelse(rm1$Is.Non.Annual. == 1, "Yes" , "No"))

rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "P1", "P")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "P3", "P")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "P4", "P")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "P5", "P")

rm1$Income.Level <- 
  replace(rm1$Income.Level, rm1$Income.Level == "Z", "Unclassified")

rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "Q", "High")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "P", "High")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "O", "High")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "N", "High")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "M", "High")

rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "L", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "K", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "J", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "I", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "H", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "G", "Medium")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "F", "Medium")

rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "E", "Low")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "D", "Low")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "C", "Low")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "B", "Low")
rm1$Income.Level <- replace(rm1$Income.Level, rm1$Income.Level == "A", "Low")

# 
# Group.State=AK,AL,AR,AZ,Bermuda,CA,CO,CT,FL,IA,ID,IL,IN,KS,MD,MN,MS,NC,NE,NJ,NM,
# NV,NY,OK,OR,PA,TN,TX,UT,VA,WA
# 
# Group.State=GA,HI,KY,LA,MA,MI,MO,NH,OH,PR,SC,SD,WI

```
#Data cleaning columns A to R

# removing redundant columns with dates and irrelevant info.
```{r}
rm1 <- rm1[,-c(1 ,9 ,10, 11,12 ,17,18,21,37,39,40)]
rm1 <- rm1[,-c(4)]

##data.frame(colnames(rm1)) #Returns column index numbers in table format,df=DataFrame name
```
#  Removed ID , Departure.Date , Return.Date ,	Deposit.Date ,
#Special.Pay , Early.RPL,	Latest.RPL


#Writing functions for mode
```{r}

find_mode <- function(x) 
  {
  u <- unique(x)
  tab <- tabulate(match(x, u))
  u[tab == max(tab)]
}


#Checking NA/Null and replacing with with mean/mode - > from.grade 

sum((rm1$From.Grade) == 'NA')
modeFG <- find_mode(rm1$From.Grade)
rm1$From.Grade <- replace(rm1$From.Grade,(rm1$From.Grade) == 'NA',modeFG)


#Checking NA/Null and replacing with with mean/mode - > To grade 

sum((rm1$To.Grade) == 'NA')
modeTG <- find_mode(rm1$To.Grade)
rm1$To.Grade <- replace(rm1$To.Grade,((rm1$To.Grade) == 'NA'),modeTG)


#Checking NA/Null and replacing with with mean/mode - > Travel.type

sum((rm1$Travel.Type) == 'N')
modeTT <- find_mode(rm1$Travel.Type)
rm1$Travel.Type <- replace(rm1$Travel.Type , rm1$Travel.Type == 'N' , modeTT) 
#N replaced with mode


#### 03/07/2022 New Part###################


###Data Cleaning


#############Cannot replace dates#################

sum(is.na(rm1$Poverty.Code))
modepc <- find_mode(rm1$Poverty.Code)
rm1$Poverty.Code <- replace(rm1$Poverty.Code,is.na(rm1$Poverty.Code)==TRUE,
                            modepc)


sum((rm1$CRM.Segment) == 'NA')
modecrms <- find_mode(rm1$CRM.Segment)
rm1$CRM.Segment <- replace(rm1$CRM.Segment,(rm1$CRM.Segment) == 'NA',modecrms)


sum(is.na(rm1$MDR.Low.Grade))
modemlg <- find_mode(rm1$MDR.Low.Grade)
rm1$MDR.Low.Grade <- replace(rm1$MDR.Low.Grade,is.na(rm1$MDR.Low.Grade)==TRUE,
                             modemlg)




sum(is.na(rm1$MDR.High.Grade))
sum((rm1$MDR.High.Grade) == 'NA')
modemhg <- find_mode(rm1$MDR.High.Grade)
rm1$MDR.High.Grade <- replace(rm1$MDR.High.Grade,rm1$MDR.High.Grade== 'NA',
                              modemhg)

sum(is.na(rm1$Total.School.Enrollment))
meantse <- round(mean(rm1$Total.School.Enrollment,na.rm=TRUE))
rm1$Total.School.Enrollment <- 
  replace(rm1$Total.School.Enrollment,
          is.na(rm1$Total.School.Enrollment)==TRUE,meantse)


sum(is.na(rm1$Income.Level))
modeil <- find_mode(rm1$Income.Level)
rm1$Income.Level <- replace(rm1$Income.Level,is.na(rm1$Income.Level)==TRUE,modeil)


sum((rm1$DifferenceTraveltoFirstMeeting) == 'NA')
meandtfm <-
  round(mean(as.numeric(rm1$DifferenceTraveltoFirstMeeting),na.rm=TRUE))
rm1$DifferenceTraveltoFirstMeeting <- 
  replace(rm1$DifferenceTraveltoFirstMeeting,
                            rm1$DifferenceTraveltoFirstMeeting == 'NA',meandtfm)


sum(is.na(rm1$DifferenceTraveltoLastMeeting))
sum((rm1$DifferenceTraveltoLastMeeting) == 'NA')
meandtlm <- round(mean(as.numeric(rm1$DifferenceTraveltoLastMeeting),na.rm=TRUE))
rm1$DifferenceTraveltoLastMeeting <- replace(rm1$DifferenceTraveltoLastMeeting,
                            rm1$DifferenceTraveltoLastMeeting == 'NA',meandtfm)


sum(is.na(rm1$FPP.to.School.enrollment))
sum((rm1$FPP.to.School.enrollment) == 'NA')
meanftse <- round(mean(as.numeric(rm1$FPP.to.School.enrollment),na.rm=TRUE))
rm1$FPP.to.School.enrollment <- replace(rm1$FPP.to.School.enrollment,
                            rm1$FPP.to.School.enrollment == 'NA',meanftse)


rm1$SchoolSizeIndicator <- 
  sapply(rm1$SchoolSizeIndicator, as.character, na.rm=TRUE)
sum(is.na(rm1$SchoolSizeIndicator))
modessi <- 
  find_mode((rm1$SchoolSizeIndicator))
rm1$SchoolSizeIndicator <- 
  replace(rm1$SchoolSizeIndicator,is.na(rm1$SchoolSizeIndicator) == TRUE,modessi)

unique(rm1$SchoolSizeIndicator)
```
## Cpoy of frame for RF
```{r}

rm2 <- rm1

```
```{r}
rm1$From.Grade <- as.factor(rm1$From.Grade)
rm1$To.Grade <- as.factor(rm1$To.Grade)
rm1$Travel.Type <- as.factor(rm1$Travel.Type)



rm1$Poverty.Code <- as.factor(rm1$Poverty.Code)
rm1$Region <- as.factor(rm1$Region)
rm1$CRM.Segment <- as.factor(rm1$CRM.Segment)
rm1$School.Type <- as.factor(rm1$School.Type)
rm1$MDR.Low.Grade <- as.factor(rm1$MDR.Low.Grade)
rm1$MDR.High.Grade  <- as.factor(rm1$MDR.High.Grade)
rm1$Income.Level  <- as.factor(rm1$Income.Level)
rm1$SPR.Product.Type  <- as.factor(rm1$SPR.Product.Type)
rm1$SPR.New.Existing  <- as.factor(rm1$SPR.New.Existing)

rm1$DifferenceTraveltoFirstMeeting <- as.numeric(rm1$DifferenceTraveltoFirstMeeting)
rm1$DifferenceTraveltoLastMeeting <- as.numeric(rm1$DifferenceTraveltoLastMeeting)
rm1$SchoolGradeTypeLow <- as.factor(rm1$SchoolGradeTypeLow)
rm1$SchoolGradeTypeHigh <- as.factor(rm1$SchoolGradeTypeHigh)
rm1$SchoolGradeType <- as.factor(rm1$SchoolGradeType)
rm1$GroupGradeTypeLow <- as.factor(rm1$GroupGradeTypeLow)
rm1$GroupGradeTypeHigh <- as.factor(rm1$GroupGradeTypeHigh)
rm1$GroupGradeType <- as.factor(rm1$GroupGradeType)
rm1$DepartureMonth <- as.factor(rm1$DepartureMonth)
rm1$MajorProgramCode <- as.factor(rm1$MajorProgramCode)
rm1$FPP.to.School.enrollment <- as.numeric(rm1$FPP.to.School.enrollment)
rm1$MajorProgramCode <- as.factor(rm1$MajorProgramCode)
rm1$SchoolSizeIndicator <- as.factor(rm1$SchoolSizeIndicator)

```
#Plotting data

```{r}
#plotting schoolgradetype against target
p1<-ggplot(data=rm1,aes(x=SchoolGradeType, y=Retained.in.2012., 
                        fill=Retained.in.2012.))+geom_bar( stat="identity")
p1

```

```{r}
#plotting isnonannual against target
p2<-ggplot(data=rm1, 
           aes(x=Is.Non.Annual.,y=Retained.in.2012., 
               fill=Retained.in.2012.)) +geom_bar( stat="identity")
p2
```

```{r}
unique(rm1$SchoolSizeIndicator)
#plotting schoolsize against target
p3<-ggplot(data=rm1, aes(x=SchoolSizeIndicator, 
                         y=Retained.in.2012., fill=Retained.in.2012.)) +
  geom_bar( stat="identity")
p3
```

```{r}
#plotting spr new existing against target
p4<-ggplot(data=rm1, aes(x=SPR.New.Existing,y=Retained.in.2012.,
                         fill=Retained.in.2012.)) +
  geom_bar( stat="identity")
p4
```

```{r}

p6<-ggplot(data=rm1, aes(x=Income.Level, 
                         y=Retained.in.2012., fill=Retained.in.2012.)) +
  geom_bar( stat="identity")
p6

```
```{r}
# library(ggplot2)
# Retained = rm1[which(rm1[,44]=='Retained'),]
# Not_Retained = rm1[which(rm1[,44]=="Not Retained"),]
# 
# view(Retained)
# par(mfrow =c(1,3))
# 
# hist(as.numeric(unlist(Retained[,44])),xlab="Days",ylab="",
#      main="Retained Vs Age",
#      ylim=c(0,160))
# hist(as.numeric(unlist(Not_Retained[,44])),xlab="Days",ylab="",
#      main="Not Retained Vs Age",
#      ylim=c(0,160))
# 
# hist(as.numeric(unlist(rm1[,23])),xlab="Days",ylab="",
#      main="Overall Response vs Age")

```

```{r}
## Total School Enrollment vs Retention
input_data <- rm1 [ , c("Total.School.Enrollment" ,"Retained.in.2012.")]


p7<- plot(y=input_data$Total.School.Enrollment , x=input_data$Retained.in.2012.,
     main="Enrollment vs Trips retained",ylab="Total.School.Enrollment", 
     xlab= "Retained.in.2012.")
p7


```

``` {r}
Retained = rm1[which(rm1[,44]=='Retained'),]
Not_Retained = rm1[which(rm1[,31]=="Not Retained"),]

plot(rm1[,44],main="Retention Rate",ylab="Number", 
     xlab= "Target Variable Type") 
#Finding the correlation 
```
``` {r}
par(mfrow =c(1,1))
plot(y=as.numeric(unlist(Retained[,44])),
x=as.numeric(unlist(Retained[,7])),pch=1,
  xlab="Travel.Type",ylab="R",main="Retained vs Travel Type")
  points(y=as.numeric(unlist(Not_Retained[,44])),
x=as.numeric(unlist(bad[,7])),pch=3,
  xlab="Travel.Type",ylab="Retained.in.2012.",main="")
  plot(y=as.numeric(unlist(bad[,44])),
x=as.numeric(unlist(bad[,7])),pch=3,
  xlab="Travel.Type",ylab="Retained.in.2012.",
  main="Travel.Type vs Overall Retention")
  plot(y=as.numeric(unlist(bad[,44]))
  
  
  
  
```

```{r}

# plotting correlation between numeric variables 
#table(is.na(rmNew))
#is.na(rmNew)

rmcorr2 <- select_if(rm1, is.numeric)
rmcorr3 <- as.numeric(rm1$Retained.in.2012.)
rmcorr2 <- cbind(rmcorr2,rmcorr3)

df.cor = cor(rmcorr2)
corrplot(df.cor)
apa.cor.table(rmcorr2,"APA correlation Table3.doc")


```

#Decision Tree
```{r}
#Data partitioning into train and Test data

set.seed(35)
indx <-  sample(2, nrow(rm1) , replace = T , prob = c(0.6 , 0.4)) 
train <- rm1[indx == 1 , ]
test <- rm1[indx == 2 , ]

#nrow(train)/nrow(rm1)
#nrow(test)/nrow(rm1)

###Functions for Evaluation metrics

EvaluationMatrix <-  function(TP,FP,FN,TN)
{
Accuracy <- (TP+TN)/(TP+TN+FP+FN)
Precision <-  TP/(TP + FP)
Recall <- TP/(TP +FN)
Fscore <- 2*(Recall * Precision) / (Recall + Precision)

EVM <-cbind(Accuracy,Precision,Recall,Fscore)

}
## Decision Tree 1

myFormula = Retained.in.2012. ~ .
myTree <- rpart(myFormula , data = train)
print(myTree)

rpart.plot(myTree)

# prob of positive and negative class
##predict(myTree, data = train)


# finding the error rate for train data
pred_train1 <- predict(myTree, data = train , type = "class")
mean(train$Retained.in.2012. != pred_train1) 

##length(pred_train1)
##length(rm1$Retained.in.2012.)

# finding the error rate for test data
pred_test1 <- predict( myTree, data1 = test , type = "class") 
mean(test$Retained.in.2012. != pred_test1)

##view(pred_test1)
## Evaluation Matrix
DTMatrix1 <-table(actual=as.factor(train$Retained.in.2012.), pred = pred_test1)
DTMatrix1

FinalEVM1 <- EvaluationMatrix(DTMatrix1[1,1], DTMatrix1[2,1],DTMatrix1[1,2],
                              DTMatrix1[2,2])
FinalEVM1

```
```{r}
summary(myTree)

```

## Decision tree with numeric variables
```{r}

set.seed(35)
indx <-  sample(2, nrow(rm1) , replace = T , prob = c(0.6 , 0.4)) 
train <- rm1[indx == 1 , ]
test <- rm1[indx == 2 , ]

myFormulanum = Retained.in.2012. ~ Tuition + FRP.Active  +School.Sponsor + 
  FPP+ Total.Pax + SingleGradeTripFlag + Total.Discount.Pax

myTreenum <- rpart(myFormulanum , data = train ,method="class")
print(myTreenum)
rpart.plot(myTreenum)

```
```{r}
predict(myTreenum, data = train)
##p <- predict(myTreenum,rm1,type="class")
# finding the error rate for train data
pred_trainnum <- predict( myTreenum , data = train , type = "class")
mean(train$Retained.in.2012. != pred_trainnum) 

# finding the error rate for test data
pred_testnum <- predict( myTreenum , data1 = test , type = "class") 
mean(test$Retained.in.2012. != pred_testnum) 

view(pred_testnum)

```
```{r}
## Evaluation Matrix
DTMatrixnum <- table(actual=rm1$Retained.in.2012., pred = pred_testnum)
DTMatrixnum

FinalEVMnum <- 
  EvaluationMatrix(DTMatrixnum[1,1],DTMatrixnum[2,1],
                   DTMatrix1[1,2], DTMatrixnum[2,2])
FinalEVMnum

```
```{r}
summary(myTreenum)

```


## Decision Tree myTreenum2
```{r}
# pruning with gini split 
myTreenum2 <- rpart(myFormula , data = train  , parms =list (split = "gini") ,
                    control = rpart.control(minsplit = 6 , minbucket = 6 , 
                                            cp = 0.01 ))


rpart.plot(myTreenum2)

# finding the error rate for train data
pred_trainnum2 <- predict( myTreenum2 , data = train , type = "class")
mean(train$Retained.in.2012. != pred_trainnum2) 

# finding the error rate for test data
pred_testnum2 <- predict( myTreenum2 , data = test , type = "class") 
mean(test$Retained.in.2012. != pred_testnum2)

view(pred_testnum2)

```
```{r}
## Evaluation Matrix
DTMatrixnum2 <- table(actual=train$Retained.in.2012., pred = pred_testnum2)
DTMatrixnum2

FinalEVMnum2 <- EvaluationMatrix(DTMatrixnum2[1,1], DTMatrixnum2[2,1],
                                 DTMatrixnum2[1,2],DTMatrixnum2[2,2])
FinalEVMnum2

```
```{r}
summary(myTreenum2)


```

## Random Forest

``` {r}

library(randomForest)

rf<- randomForest(Retained.in.2012.~.,data = rm1,mtry = sqrt(ncol(rm1)-1),
                   ntree = 300,proximity = T,importance = T)
              

print(rf)
## The OOB error rate of our random forest model is .1972

```

```{r}
attributes(rf)
```

```{r}
plot(rf)
```

```{r}
##rf$err.rate

##  important variables based on MeanDecreaseAccuracy.

library("dplyr")
IMP <- importance(rf, type = 1)
IMP
```

```{r}
subset(IMP, IMP[] >  10)
##filter(IMP, MeanDecreaseAccuracy >= 10)

varImpPlot(rf)


rf$proximity


rf3 <- randomForest(Retained.in.2012. ~ From.Grade + To.Grade +
                      Is.Non.Annual.+ FRP.Active+ CRM.Segment+ MDR.High.Grade
+ Total.School.Enrollment + SPR.New.Existing + FPP + Total.Pax +
  SingleGradeTripFlag + FPP.to.PAX, data = rm1,
                   mtry = sqrt(ncol(rm1)-1), ntree = 300,
                   proximity = T, importance = T)

print(rf3)
```

```{r}

rf4 <- randomForest(Retained.in.2012. ~ Is.Non.Annual.+SPR.New.Existing + SingleGradeTripFlag, data = rm1,
                   mtry = sqrt(ncol(rm1)-1), ntree = 300,
                   proximity = T, importance = T)

print(rf4)

head(rf$predicted)


head(rf$votes)

```


```{r}

ind <- sample(2, nrow(rm1), replace = T, prob = c(0.7, 0.3))
trainrf <- rm1[ind == 1, ]
Validation <- rm1[ind == 2, ]
pr.err <- c()
for(mt in seq(1,ncol(trainrf)))
   {
library(randomForest)
rf1 <- randomForest(Retained.in.2012.~.,data = trainrf, ntree = 100,
mtry = ifelse(mt == ncol(trainrf),
mt-1, mt))
predicted <- predict(rf1, newdata = Validation, type = "class")
pr.err <- c(pr.err,mean(Validation$Retained.in.2012. != predicted))
}

bestmtry <- which.min(pr.err)

bestmtry


```


```{r}
# Plotting confusion matrix

table(rf$predicted, rm1$Retained.in.2012., dnn = c("Predicted", "Actual"))


```



```{r}
# plotting confusion Matrix

confusionMatrix(rf$predicted, rm1$Retained.in.2012., positive = "Retained")             


```



```{r}
score <- rf$votes[, 2] 

pred <- prediction(score, rm1$Retained.in.2012.)

### plotting Gain chart
```


```{r}
perf <- performance(pred, "tpr", "rpp") 

plot(perf)
```


#plotting ROC curve

```{r}
perf <- performance(pred, "tpr", "fpr")
pred
plot(perf)
```



## Finding area under the curve (AUC)


```{r}
auc <- unlist(slot(performance(pred, "auc"), "y.values"))
auc
```


```{r}
# Determine the best cut-off point
perf <- performance(pred, "tpr", "fpr")

opt.cut <- function(perf)
  
  { 
  cut.ind <- mapply(FUN = function(x,y,p){d=(x-0)^2+(y-1)^2 
  ind<- which(d==min(d)) 
  c(recall = y[[ind]],specificity = 1-x[[ind]],cutoff = p[[ind]])}
    
    , perf@x.values, perf@y.values,perf@alpha.values)
    }
opt.cut



best_cut <- opt.cut(perf$fpr,perf$tpr,perf$pred)

cut.ind 

```

## CrossValidation in R
```{r}

#pacman::p_load(pacman,party,psych,rio,tidyverse)
#library("ISLR")
## Randomization ## Step 1 : Cut into K different folds

k<- 5 ## number of K folds
nmethod <- 1 ## number of methods used for comparison

folds <- cut(seq(1, nrow(rm1)), breaks = k, labels =FALSE)

## Matrix formulation
model.err <- matrix (-1, k, nmethod , 
                     dimnames = list(paste0("Fold", 1:k),c("LogitReg")))

###For loop for different models
for ( i in 1:k)
{
  testindexes <- which (folds == i , arr.ind = TRUE)  ## Track of test instances
  
  ## test and train data sets
  test <- rm1 [testindexes, ]
  train <- rm1 [-testindexes, ]
  
  ## model
  
  LogitModel <- glm(Retained.in.2012. ~ ., data = train , family = "binomial")
  ## will return probability of prediction
  pred <- predict(LogitModel , newdata = test, type = "response")
  
  pred_class <- as.factor(ifelse( pred >= 0.5, "Yes", "No"))
  
 ## error rate if test instances are not equal to Train for that fold
  model.err[i] <- mean(test$Retained.in.2012. != pred_class)
  
}

view(model.err)


```
